Robotic Cart System

### 2021-05-12 parts/30-implementation.tex
Update 30-implementation.tex
Edits

For the implementation of this project we had to start from scratch since this was a new project concept introduced by our advisor Dr. Miah. There have been senior projects in the past that have used XBees to get signal strength but there is very little overlap between these projects to substantiate where our project needed to start from. For this project we had to first build a mobile robot and a remote to use for testing. We then had to build a code base to control the mobile robot that was then implemented with our test algorithms.

@@

For this project we needed a Remote Target and Smart Robotic Cart that we designed and implemented from off the shelf components.  As mentioned above in section \ref{sec:System Components}, some of our components came from what the school already owned as well as some we had to buy specifically for this project listed in \autoref{tab:Partslablist} and \autoref{tab:Partslist}.

\vspace*{12pt}
\noindent
Since the school already owned the Budget Bot chassis, we decided to build our Smart Robotic Cart with them. The Budget Bot chassis needed to be modified slightly to work with our project. The main change we made was swapping out the motors that came with the Budget Bot for Pololu 27D Metal Gear motors since the original motors have a max speed of 212 RPM or 1.09m/s and the new motors have a max speed of 530 RPM or 2.72m/s when using the wheels with a diameter of 98mm. By switching out the motors we are able to achieve our goal of matching an average person's walking speed of 1.5m/s. The other modifications to the chassis are a hard power switch to directly cut off power to the XBee modules in the reflector and a power indicator LED to let us know when this switch was on.

\vspace*{12pt}
\noindent
As shown in Fig. \ref{fig:FinalizedRobot}, our next step was to attach the BeagleBone Blue microcomputer, XBee reflector array assembly, and breadboard to the top of the robot. We also installed a 2-cell LiPo battery inside the chassis of the mobile cart that delivers power to the BeagleBone Blue directly and the breadboard through the switch.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\textwidth]{figs/img/Finalized_robot.png}
    \caption{Overall Prototype of the Robotic Cart}
    \label{fig:FinalizedRobot}
\end{figure}

The power supplied to the breadboard is sent through a regulator circuit to drop it down from the 7.4V of the LiPo to 3.3V of the XBee. This circuit is also used on the remote which consists of a 7.4V LiPo battery and the XBee module with voltage regulator in between. This voltage regulator is built out of a LM117 regulator and a 10uF ceramic capacitor between the input and output pins of the regulator as shown in Fig. \ref{fig:PowerConverter}.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\textwidth]{figs/img/PowerConverter.png}
    \caption{Final Version of the Robotic Cart}
    \label{fig:PowerConverter}
\end{figure}

\vspace*{12pt}
\noindent
The reflector array assembly from \autoref{sec:customReflector} was mounted on a stepper motor that was then attached to the robot chassis using a 3D printed bracket. This bracket was then attached to the chassis using bolts. Another feature of this bracket is that it had a stop block built into the top of it to automatically zero the reflector array when the robot starts up.

\vspace*{12pt}
\noindent
The Xbee modules from the reflector array posed a bit of a problem when it came to connecting them to the BeagleBone Blue. The BeagleBone Blue has five UART ports if one were the three standard UART ports and tow others found in the USB and UART-GPS. Unfortunately though this does not work since UART port zero is tied to the council used to communicate with it from a computer. Since this port is reserved for this function that reduces the number of usable ports down to four and we need to have five XBees in these ports. Our solution to this was to use two of the GPIO pins, two of the UART ports, and a two-way multiplexer. With this setup we can directly connect one of the UARTs to the top XBee and then rout the other four side XBee modules through the MUX so only one UART port is needed for them.

@@

For the project we needed some base functionality to use with the main follower program so it can interact with the other components in the system. The BeagleBone Blue already has a set of ports on it that we can access and control using the Robot Control Library from Strawson Design ~\cite{Robot_Control_Library}.

\vspace*{12pt}
\noindent
For the project we also built some custom libraries on top of the Robot Control Library to handle XBee Frames, AT Commands, and the stepper motor. The XBee Frames library takes a given block of data containing our message and then packages it into a XBee Frame to send over UART to the XBee module we want to interact with. The XBee communications library also handles received messages from the XBee module and validates the received frames integrity and extracts the message data from it. On top of the XBee communications library we also have a library that generates AT Commands to package in the XBee Frames. The AT Command library also handles extracting response data from the AT Response Command structure and validates it.

@@

\vspace*{12pt}
\noindent
The final custom library is the stepper motor control library. This library had to be written ourselves since instead of using a dedicated stepper motor controller for our project we were using two of the regular DC motor control ports that are build into the BeagleBone Blue. The library handled translating how many steps to turn into the phase states to be sent to the DC motor ports that are connected to the stepper motor. The library also helped to keep track of basic information related to the stepper motor such as what its current angle should be.

@@

In this project after we had the Robotic Cart, Remote Target, and a code base to handle the specifics we started testing different variants of our algorithm explained in \autoref{sec:locAndNavAlgos}. There were two main types of variants we put together, one type the stepper motor is locked preventing the reflector from turning and in the other we use the stepper motor to sweep through a set of angles.

@@

The first type of test we ran was where the robot would zero out the arrays rotation with the stepper motor then move in nine degree increments taking measurements as it went. A sweep ends when the motor has turned 81 degrees since at that point, with the four sides of the reflector, a full 360 degrees has bean scanned.

\vspace*{12pt}
\noindent
This method offers us a sufficiently dense set of data to base our angle predictions off of but at the cost of having to wait until a entire sweep of the reflectors is completed. With this data we first put together a simple test that would continuously be sweeping and moving at the same time. Though this version did successfully follow the remote it had some errors in the robot's navigation trajectory. For example, the robot would correctly turn towards the remote, however, if it picked up a stronger signal from the XBee reverberations, it would drive off in a different direction. The robot would eventually find its way back into alignment and resume moving towards the remote.

\vspace*{12pt}
\noindent
The next version that used a rotating reflector, as well as the final version, works mostly the same as the first version but with some improvements to its navigation. The first big fix is that we determined that the oscillation we were seeing in the first test were a result of turning while also rotating the reflector which would add additional rotation to the measurements in global scope. Due to how our robot is designed we can only rotate the reflector array 90 degrees but to properly fix this rotation issue we would need to rotate the reflector more or less during a sweep to compensate for the robots rotation. Our compromise was simply to allow the robot to always move forward but to alternate between getting measurements and then rotating the robot based on the measurements. In this version some additional windowed filters to average out the angle measurements were added, which did help to reduce the effects of random angles from noise in the system. We also applied offsets to each of the directional receivers revived signal strengths based off the data that we had collected while testing it. This offset was needed due to each side having a different minimum that it would cap out at.

@@

The locked reflector tests were ran in between our first algorithm and our final algorithm which ultimately used a sweeping function to capture the XBee signals. These algorithms were an attempt to reduce the time needed to get a set of measurements from the reflector by zeroing its rotation and then keeping it locked in the zeroed position. Since the data from this is relatively sparse we tried three different ways to fill in the gaps in the data from only the four cardinal directions. The first of these three methods was to try and select a strongest direction that the signal was coming from and then which of its two neighbor directions had the next strongest signal. With these two strengths the algorithm would then try to interpolate between these two angles based on the difference of the strengths between them. This method could work but due to the time constraints of our project, we did not have enough time to implement and test this method.

\vspace*{12pt}
\noindent
The other two methods that we tried with the locked reflector were both different variants on machine learning algorithms based on a small pool of data we had collected. The first algorithm tested was K Nearest Neighbors then followed up by a Neural Network for our final fixed rotation test. Both of these algorithms failed to produce any meaningful results due to the fact that we had a very small pool of data to work off of compared to the large amounts of data needed to perform machine learning algorithms. These algorithms, with the small data pool size, did not perform well with the noise in the signals.

@@

In both our fixed and sweeping experiments a underlying issue is the amount of noise our system produces. The first type of noise that occurs is noise from the Multipath Effect where the signals bounce off of obstacles around it adding constructing and destructive interference randomly based off of the robots surroundings. The second noise was from internal noise in the XBees which was worse that we had expected. We managed to isolate the XBee internal noise by using an anechoic chamber where we did see all the signals strengths become stronger but the base noise from the XBees persisted. The noise coming from the XBees tends to be about 2 to 6 dBm on average. The change from facing towards the remote then away from the remote is about 13 to 15 dBm. These ranges result in the occasional measurement that flip flops which reflector is actually facing the remote. The noise can be seen in our test measurements we collected where we, at set rotations, record a burst of 300 measurements as seen in Fig. \ref{fig:SensorDataGraphs}

@@

\subsection{Distance}
This project initially planned to use the top XBee modules signal strength to determine the distance to the remote.  In practice, though, it was determined to be practically impossible with our setup.  The free space path loss equation was used as a base equation to work from for implementing this feature in the project.  The issue arises initially from that the free space path loss failed to return a usable distance by itself whenever any form of obstacle ends up in the line of sight path to the remote.  The free space path loss equation also is thrown off by any reflective surfaces around it due to the multipath effect.  These issues could be potentially solved by Simultanius Localization and Mapping algorithms like EKF-SLAM.  Unfortunately, this approach also does not work since it relies on a known global reference point that is absent in this project design. Since within the allotted time for the project, no viable solution was found, it was decided that the distance measurement would be put on hold for future work on the project

@@

Before constructing the physical robot prototype, a simulation was performed using a commercial robot simulator CoppeliaSim. However, since RF signal behavior depends highly on the environment, the system could not be fully simulated. This section explains the steps taken to simulate the proposed robotic cart.

\vspace*{12pt}
\noindent
First, a model of the Budget Bot chassis was created in CoppeliaSim. The model is shown in Fig. \ref{fig:budgetBotModel}. The model was designed with the same dimensions as the physical chassis to accurately simulate the robot kinematics. Details on modeling a robot chassis in CoppeliaSim can be found in \autoref{ch: coppSimModeling}. Although \autoref{ch: coppSimModeling} explains the modeling of a robot chassis that is different than the Budget Bot chassis, the concepts are the same for modeling any robot chassis.

\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{figs/img/budgetBotModel.png}
    \caption{Model of Budget Bot Chassis}
    \label{fig:budgetBotModel}
\end{figure}

\vspace*{12pt}
\noindent
MATLAB code was written to control the simulation. The actual distance between the robot and the remote was measured, then random noise was added with a mean of 0 and a standard deviation of 0.07. This noisy measurement was then used in the navigation algorithm to determine how to drive the robot (see \autoref{subsec:navAlgo}). An image of the simulation is shown in Fig. \ref{fig:coppSimExample}, where the blue sphere represents the remote, and the green dot represents the target point.
\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figs/img/coppSimExample.png}
    \caption{CoppeliaSim Simulation}
    \label{fig:coppSimExample}
\end{figure}

>>>>

Since this project was a new concept, the implementation had to start from scratch. Although there have been projects in the past that have used XBees to get signal strength, none of them used it in the same way as this project. For this project a mobile robot and a remote first had to be built to use for testing. Then a code base needed to be created to control the mobile robot according to the design algorithms.

@@

For this project, a Remote Target and Smart Robotic Cart were designed and implemented from off-the-shelf components.  As mentioned above in section \ref{sec:System Components}, some of the components were already available at Bradley University, and others had to be purchased specifically for this project. The parts are listed in \autoref{tab:Partslablist} and \autoref{tab:Partslist}.

\vspace*{12pt}
\noindent
Since the school already owned the Budget Bot chassis, it was a good choice for the base of the  Smart Robotic Cart. However, the Budget Bot chassis was modified slightly to work for this project. The main change was swapping out the motors that came with the Budget Bot for Pololu 27D Metal Gear motors since the original motors have a max speed of 212 RPM or 1.09m/s and the new motors have a max speed of 530 RPM or 2.72m/s when using the wheels with a diameter of 98mm. By switching out the motors enabled the robot to move faster to make it better able to achieve the goal of matching an average person's walking speed. The other modifications to the chassis were a hard power switch to directly cut off power to the XBee modules in the reflector and a power LED to indicate when this switch was on.

\vspace*{12pt}
\noindent
The next step was to attach the BeagleBone Blue microcomputer, XBee reflector array assembly, and breadboard to the top of the robot. A 2-cell LiPo battery was also installed inside the chassis of the mobile cart to provide power to the BeagleBone Blue directly and the breadboard through the switch. The power supplied to the breadboard is sent through a regulator circuit to drop it down from the 7.4V of the LiPo to 3.3V of the XBee. This circuit is also used on the remote which consists of a 7.4V LiPo battery and the XBee module with voltage regulator in between. This voltage regulator is built out of a LM117 regulator and a 10uF ceramic capacitor between the input and output pins of the regulator. The circuit diagrams for the robot and remote are shown in Figs. \ref{fig:robotCircuit} and \ref{fig:remoteCircuit}.
\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{figs/robotCircuit.pdf}
    \caption{Circuit Diagram for Robotic Cart}
    \label{fig:robotCircuit}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.7\textwidth]{figs/remoteCircuit.pdf}
    \caption{Circuit Diagram for Remote}
    \label{fig:remoteCircuit}
\end{figure}

\vspace*{12pt}
\noindent
The reflector array assembly from \autoref{sec:customReflector} was mounted on a stepper motor that was then attached to a 3D printed bracket. This bracket was then attached to the chassis using M3 screws. Another feature of this bracket is that it had a stop block built into the top  to allow the robot to automatically initialize the reflector array to the zero position when the robot starts up. This is accomplished by commanding a turn of 90\textdegree and allowing the reflectors to hit the stop block and be held there until this turn is complete.

\vspace*{12pt}
\noindent
The Xbee modules from the reflector array posed a bit of a problem when it came to connecting them to the BeagleBone Blue. The BeagleBone Blue has three standard UART ports and two others found in the USB and UART-GPS, which makes a total of five UARTs. Unfortunately not all five ports can be used to communicate with XBees since UART0 is used to provide communication with a computer through the console. Since port 0 is reserved for this function, the number of usable ports is only four, but the project requires communication with five XBees. The solution to this problem was to use two of the GPIO pins, two of the UART ports, and a dual 4-channel multiplexer. One of the UARTs can be directly connected to the top XBee, and the other UART can be routed through the multiplexer to the four side XBee modules. Then two UART ports are used to communicate with all five XBees.

\vspace*{12pt}
\noindent
Instructions for assembling the robot can be found in \autoref{ch: assemblyInstructions}. Therein, the sequence of steps is explained in detail with pictures to show the state of the robot. The finished prototype robot and remote are shown in Fig. \ref{fig:finishedPrototypes}.

\begin{figure}[H]
    \centering
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/img/Finalized_robot.png}
        \captionsetup{width=\textwidth}
        \caption{Robotic Cart Prototype}
        \label{fig:overallPrototype}
    \end{subfigure}
    \begin{subfigure}[t]{0.35\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/remote.pdf}
        \captionsetup{width=\textwidth}
        \caption{Remote Prototype}
        \label{fig:remotePrototype}
    \end{subfigure}
    \caption{Finished Prototypes}
    \label{fig:finishedPrototypes}
\end{figure}

@@

For the project some base functionality was needed to use with the main follower program so it could interact with the other components in the system. The BeagleBone Blue already has a set of ports on it that can be accessed and controlled using the Robot Control Library from Strawson Design ~\cite{Robot_Control_Library}.

\vspace*{12pt}
\noindent
Some custom libraries were built on top of the Robot Control Library to handle XBee Frames, AT Commands, and the stepper motor control. The XBee Frames library takes a given block of data containing the message and then packages it into a XBee Frame to send over UART to the XBee desired module. The XBee communications library also handles received messages from the XBee module and validates the received frame's integrity and extracts the message data from it. On top of the XBee communications library there is a library that generates AT Commands to package in the XBee Frames. The AT Command library also handles extracting response data from the AT Response Command structure and validates it.

@@

\vspace*{12pt}
\noindent
The final custom library is the stepper motor control library. This library had to be written since instead of using a dedicated stepper motor controller, two of the regular BBBlue DC motor control ports were used to power the stepper motor. The library handled translating how many steps to turn into the phase states to be sent to the DC motor ports that are connected to the stepper motor. The library also helped to keep track of basic information related to the stepper motor such as what its current angle should be.

@@

After the Robotic Cart, Remote Target, and code base were built, several different variants of the algorithms explained in \autoref{sec:locAndNavAlgos} were tested. There were two main types of variants tested. In one variant, the stepper motor is locked, preventing the reflector from rotating. In the other variant, the stepper motor is used to sweep through the angles.

@@

The first type of test was where the robot would initialize the reflector array to the zero point with the stepper motor, then rotate in nine degree increments taking measurements as it went. A sweep ends when the motor has turned 81 degrees since at that point, with the four sides of the reflector, a full 360 degrees has been scanned.

\vspace*{12pt}
\noindent
This method offers a sufficiently dense set of data to base the angle predictions off of, but at the cost of having to wait until a entire sweep of the reflectors is completed for a single estimation of the remote location. The first attempt with this method was a simple test that would continuously sweep the reflectors and move the robot at the same time. Though this version did eventually make its way toward the remote, it had some errors in the robot's navigation trajectory. For example, the robot would correctly turn towards the remote, however, if it picked up a stronger signal from the XBee reverberations, it would drive off in a different direction. The robot would eventually find its way back into alignment and resume moving towards the remote.

\vspace*{12pt}
\noindent
The next version that used a rotating reflector, as well as the final version, works mostly the same as the first version, but with some improvements to the navigation. It was determined that the oscillations in the robot's trajectory in the first test were a result of turning the robot while also rotating the reflector. This adds additional rotation to the measurements in the global scope. Due to the design of the robot, the reflector array can only be rotated 90 degrees, but to properly fix this rotation issue the reflector array would need to be rotated more or less during a sweep to compensate for the robot's rotation. The solution was simply to alternate between sweeping the reflector and rotating the robot, all the while allowing the robot to always move forward. The rotation of the robot was limited to 15\textdegree before another measurement would be taken. In this version some additional windowed filters to average out the angle measurements were added, which did help to reduce the effects of random angles from noise in the system. Based on data collected in an anechoic chamber, offsetsfor each of the directional receivers were applied to try to convert the received signal strengths to use the same baseline. This offset was needed since each XBee would receive slightly different signal strengths when it was pointed directly at the remote.

@@

The locked reflector tests were run in between the first algorithm and the final algorithm which ultimately used a sweeping function to capture the XBee signals. The locked reflector algorithms were an attempt to reduce the time needed to get a set of measurements from the reflector by zeroing its rotation and then keeping it locked in the zero position. Since the data from this is relatively sparse, three different methods for estimating the angle of the remote were attempted. The first of these three methods was to try to select the direction that the signal was coming strongest from and then which of its two neighbor directions had the second strongest signal. With these two strengths the algorithm would then try to interpolate the angle based on the difference of the strengths between them. This method could possibly work, but due to the time constraints of the project, there was not enough time to implement and test this method.

\vspace*{12pt}
\noindent
The other two methods that were tried with the locked reflector were both different variants on machine learning algorithms. A small pool of data was collected both in an anechoic chamber and in a normal operating environment. The first algorithm attempted to use the K Nearest Neighbors algorithm to estimate the angle of the remote based on the relative signal strengths received by the directional XBees. The second algorithm used a neural network to predict the angle. Both of these algorithms failed to produce meaningful results, probably due to the fact that there was a very small pool of data to work with compared to the large amounts of data needed to perform machine learning algorithms. The noise in the signals proved too much for these algorithms to handle elegantly. If data were collected in many operating environments, machine learning techniques may be able to yield favorable results.

@@

In both the fixed and sweeping experiments, an underlying issue was the amount of noise in the system. The first type of noise that occurs is noise from the multipath effect, where the signals bounce off obstacles in the environment, adding constructing and destructive interference randomly based on the robot's surroundings. The second source of noise was internal noise in the XBees, which was worse than what was expected. The XBee internal noise was isolated using an anechoic chamber where all the signals strengths did become stronger, but the base noise from the XBees persisted. The noise coming from the XBees tends to be about 2 to 6 dBm on average. The change from facing towards the remote then away from the remote is about 13 to 15 dBm. These ranges result in the occasional measurement that flip flops which reflector is actually facing the remote. The noise can be seen in the test measurements that were collected where 300 measurements were taken at several intervals around the robot as seen in Fig. \ref{fig:SensorDataGraphs}.

@@

\subsection{Distance}
This project initially planned to use the top XBee module's signal strength to determine the distance to the remote. In practice, however, it was determined to be nearly impossible with the current setup. The free-space path loss equation was used as a base equation to attempt to implement this feature in the project. One problem is that the free-space path loss formula is for use in free space, so it fails to yield the correct distance whenever any form of obstacle ends up in the line-of-sight path to the remote. The free-space path loss formula is also thrown off by any reflective surfaces around it due to the multipath effect. These issues could be potentially solved using a simultaneous localization and mapping algorithm such as EKF-SLAM.  Unfortunately, this approach would be very difficult since it relies on a known global reference point, but the robot in this project has no such global reference. It was decided that the distance measurement would be put on hold for future work on this project.

@@

Before constructing the physical robot prototype, a simulation was performed using a commercial robot simulator, CoppeliaSim. However, since RF signal behavior depends highly on the environment, the system could not be fully simulated. This section explains the steps taken to simulate the proposed robotic cart.

\vspace*{12pt}
\noindent
First, a model of the Budget Bot chassis was created in CoppeliaSim. The model is shown in Fig. \ref{fig:budgetBotModel}. The model was designed with the same dimensions as the physical chassis to accurately simulate the robot kinematics. Details on modeling a robot chassis in CoppeliaSim can be found in \autoref{ch: coppSimModeling}. Although \autoref{ch: coppSimModeling} explains the modeling of a robot chassis that is different than the Budget Bot chassis, the concepts are the same for modeling any robot chassis.
\begin{figure}[H]
    \centering
    \includegraphics[width=0.4\textwidth]{figs/img/budgetBotModel.png}
    \caption{Model of Budget Bot Chassis}
    \label{fig:budgetBotModel}
\end{figure}

\noindent
MATLAB code was written to control the simulation. The actual distance between the robot and the remote was measured, then random noise was added with a mean of 0 and a standard deviation of 0.07. This noisy measurement was then used in the navigation algorithm to determine how to drive the robot (see \autoref{subsec:navAlgo}). An image of the simulation is shown in Fig. \ref{fig:coppSimExample}, where the blue sphere represents the remote, and the green dot represents the target point.
\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\textwidth]{figs/img/coppSimExample.png}
    \caption{CoppeliaSim Simulation}
    \label{fig:coppSimExample}
\end{figure}

### 2021-05-12 parts/40-conclusion_and_future_work.tex
Updated Final Report
Edits

%======================================================================
\chapter{Conclusion and Future Work}
\label{ch: Chapter6}
%======================================================================

@@

From what we have seen in this project we would conclude that the robotic cart can indeed successfully follow the remote target radio.

\todo[inline]{Complete the conclusion section}

@@

\todo[inline]{Complete the future work section}

>>>>

%======================================================================
\chapter{Conclusion and Future Work}
\label{ch: Chapter6}
\label{ch: conclusionAndFuture}
%======================================================================

@@

This project shows that it is possible to use signal strength alone to make a mobile cart follow a remote target. A functional design for a mobile cart was developed and tested. In these tests, it was concluded that with the robot's current design, it would be extremely difficult to calculate an accurate distance to the remote from the signal strength alone. Therefore, the current design follows the target remote based on angle measurements alone. Due to the limitation of not having a usable distance value, the current implementation is unable to dynamically adjust its behavior based on proximity to the remote. One such planned parameter was the robot's velocity, which would have been reduced as the robot approached the remote target to prevent it from running into the user. Based on the literature review, it was determined that the Smart Robotic Cart design from this project is more cost-effective than most, if not all, of the existing solutions. It was shown that the robot could successfully track the remote target even when obstacles were obstructing the line-of-sight path between the robot and remote.

@@

Although the robotic cart prototype did successfully follow the remote based on signal strength alone, there is still much to be desired. The first item that would need to be addressed is a proper obstacle avoidance system. For the current robotic cart prototype, it was initially planned to have the robot avoid collision with the user by using the distance between the robot and remote, but this was dropped due to the inaccuracy of the distance measurement. This user avoidance could be incorporated into an obstacle detection and avoidance system in a future project, most likely using infrared or sonar sensors mounted on the robot. This is a necessary continuation of this project since, as it currently stands, it can detect and follow the remote through obstacles but will attempt to drive in a straight path towards the remote despite the obstacle between them.

\vspace*{12pt}
\noindent
The project also requires more overall tuning in any future work that is done on it. The two main places that need more tuning are the weights used to normalize the signal strengths out of the reflector array and the specs of the reflector array's design to optimize its performance. The values for normalizing the signal strengths coming out of the array currently are based on a relatively small and limited set of recorded data from the robot. For a future extension of this project, more measurements would be required to better determine the quality of the data coming out of each reflector. These values would most likely be obtained by taking many measurements in an anechoic chamber, which was also used for the current smaller set of sensor data. The data currently is only being used to calculate a base offset for each reflector's strength, though with enough data, it may be possible to use the top radio module's strength to adjust for overall degradation to the signal strength. The reflectors themselves also most likely need to be redesigned again. During testing, it was noted that the difference from facing the target to facing away from the target is only slightly greater than the average signal strength measurement noise.

\vspace*{12pt}
\noindent
Another problem that needs to be addressed in this project is determining a reasonably accurate distance measurement. The problem with distance stems from the fact that the locations remote and robot are relative to each other, so there is no global reference point that can be used to stabilize the measurements. The second problem is that the only way with the signal strength to get distance is to use a version of free-space path loss, which fails when the user stands between the remote and the robot. For this, two possible solutions were thought up after it was determined that signal strength alone would not work. These solutions were also determined to be outside the scope of what could be reasonably achieved within the allotted project time. The two possible solutions are to use signal strength with multi-frequency radio modules or to use the travel time of the message from the robot. The multi-frequency approach would still use signal strength but would potentially allow for a profile to be put together from the signal strength of each frequency to try and ignore the interference from objects. The other approach of using a message's travel time has been shown to work in such applications as GPS over large distances. This approach may work since the speed of the radio signal is generally less affected by objects in its path than signal strength is. The main challenge with this approach would be getting a sufficiently accurate time measurement for short distances. If either of these approaches to determining distance ended up working, then the algorithm could be more dynamic in its behavior and interpretation of the signal strengths.
